---
title: "case_study"
author: "Eric Morris"
date: "10/9/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

Load data sets

```{r}
library(p8105.datasets)

data(nyc_airbnb)
```

Rename/clean some things

```{r}
nyc_airbnb =
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(boro = neighbourhood_group)
```

## Some questions 

* Does rating vary by neighborhood, room type, or both?
* How is price related to other variables?
* Where are rentals located?

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = longitude, y = latitude, color = boro)) +
  geom_point() 

nyc_airbnb %>% 
  filter(boro == "Manhattan") %>% 
  ggplot(aes(x = longitude, y = latitude, color = price)) +
  geom_point(alpha = .2) +
  facet_grid(~room_type) 
```

* What's the most/least expensive area?
* Which listings have the most unfilled days?
* Which are has the highest density of listings? 
* What are some host characteristics? How many listings? What's associated with ratings? 

```{r}
nyc_airbnb %>% 
  select(boro, neighbourhood, price) %>% 
  filter(boro == "Brooklyn") %>% 
  group_by(neighbourhood) %>% 
  summarize(n_listings = n(),
    mean_price = mean(price, na.rm = TRUE),
            median_price = median(price, na.rm = TRUE)) %>%
  top_n(5) %>% View

nyc_airbnb %>% 
  select(boro, neighbourhood, price) %>% 
  filter(boro == "Brooklyn") %>% 
  group_by(neighbourhood) %>% 
  summarize(n_listings = n(),
            mean_price = mean(price, na.rm = TRUE),
            median_price = median(price, na.rm = TRUE)) %>%
  arrange(mean_price)%>% View

nyc_airbnb %>% 
  select(neighbourhood, price) %>% 
  group_by(neighbourhood) %>% 
  summarize(mean = mean(price)) %>%
  top_n(-5) %>% View
```

